Conjure: Summoning Proxies from Unused Address Space

### 2019-09-25 paper/paper.tex
remove ack todos

\begin{acks}
  The authors thank the incredible partner organizations that have
  made deployment of Refraction Networking a reality, especially Merit
  Network and Psiphon. We also thank \TODO{anyone else?} the
  University of Colorado IT Security and Network Operations
  staff. This material is based in part upon work supported by the
  U.S. National Science Foundation under Awards \TODO{others?}
  CNS-1518888 and OAC-1925476.
\end{acks}

>>>>

\begin{acks}
  The authors thank the incredible partner organizations that have
  made deployment of Refraction Networking a reality, especially Merit
  Network and Psiphon. We also thank the
  University of Colorado IT Security and Network Operations
  staff. This material is based in part upon work supported by the
  U.S. National Science Foundation under Awards
  CNS-1518888 and OAC-1925476.
\end{acks}
